---
title: "inro to function in R"
author: "Abdel Samea Ahmed"
date: "12/14/2020"
output: html_document
---

Intro to function in R {.tabset}
===================================================
## __function definition__
 function is a group of instructions that takes input and uses them to compute other values and return results.
 **example:**
 create function called oddcount to calculate the count of odd numbers in vector of integer
 *solution*

```{r setup, include=T}
knitr::opts_chunk$set(echo = TRUE)
# counts the Number of odd numbers
oddcount <- function(x){
  #assiegn k to 0
  k <- 0
  for(n in x)
    if (n%%2==1){
      k <- k+1
    }
    return(k)
  
  
}
# count the odd numbers in y <- c(1,2,3)

y <- c(1,2,3,7,9)
oddcount(y)

```

## __Function parts__

An R function is created by using the keyword function. The basic syntax of an R function definition is as follows:
function_name <- function(arg_1, arg_2, ...) {
   Function body 
}

***
Function Components
The different parts of a function are −

Function Name − This is the actual name of the function. It is stored in R environment as an object with this name.

Arguments − An argument is a placeholder. When a function is invoked, you pass a value to the argument. Arguments are optional; that is, a function may contain no arguments. Also arguments can have default values.

Function Body − The function body contains a collection of statements that defines what the function does.

Return Value − The return value of a function is the last expression in the function body to be evaluated.

R has many in-built functions which can be directly called in the program without defining them first. We can also create and use our own functions referred as user defined functions.

*Simple Example:

```{r}
# create function take 2 arguments and 
  #returns power of 
powerof <- function(x,y){
  result=x^y
  return(result)
}

powerof(2,2)

## we can set a default value for one of the 2 arguments
powerof <- function(x, y = 4){
  result = x^y
  print(paste(x , "raised to 4 is =:" ,result ))
}

powerof(3)

```



## __Builtin Functions__

Simple examples of in-built functions are seq(), mean(), max(), sum(x) and paste(...) etc. They are directly called by user written programs. You can refer most widely used R functions

```{r echo=T}
# Create a sequence of numbers from 32 to 44.
print(seq(32,44))

# Find mean of numbers from 25 to 82.
print(mean(25:82))

# Find sum of numbers frm 41 to 68.
print(sum(41:68))

```

